\documentclass[11pt]{article}
\usepackage{amsmath}

\begin{document}
	
	\tableofcontents
	\newpage
	
	\setcounter{section}{2}
	\section{}
	
	\subsection{}
	\subsection*{Exercise}
	Devise three example tasks of your own that fit into the MDP framework,
	identifying for each its states, actions, and rewards. Make the three examples as different
	from each other as possible. The framework is abstract and flexible and can be applied in
	many different ways. Stretch its limits in some way in at least one of your examples.
	\subsection*{Solution}
	\begin{enumerate}
		\item \textbf{Chess Engine}: An agent which plays game of chess. States include piece positions, castling and en-passant rights. Actions are legal moves from the current position. Rewards are +1 for win, -1 for loss and 0 for draw.
		\item \textbf{Self-Driving Car}: An autonomous vehicle agent. States include car location, street position, and pedestrian presence. Actions include acceleration, braking and steering. Rewards are positive for approaching destination, negative for time passing, collisions, pedestrian hits, gas depletion, or rule violation.
		\item \textbf{Pianist}: An agent that plays the piano like a musician. States are current note positions in the musical sequence. Actions are piano key presses. Rewards measure how well the music is played.
	\end{enumerate}
	
	\subsection{}
	\subsection*{Exercise}
	Is the MDP framework adequate to usefully represent all goal-directed learning tasks? Can you think of any clear exceptions?
	\subsection*{Solution}
	No, it's not adequate to usefully represent all goal-directed learning tasks. Tasks where rewards cannot be properly defined. For example, an agent attempting to solve unsolved mathematics problems.
	
	\subsection{}
	\subsection*{Exercise}
	Consider the problem of driving. You could define the actions in terms of the accelerator, steering wheel, and brake, that is, where your body meets the machine.
	Or you could define them farther out—say, where the rubber meets the road, considering
	your actions to be tire torques. Or you could define them farther in—say, where your
	brain meets your body, the actions being muscle twitches to control your limbs. Or you
	could go to a really high level and say that your actions are your choices of where to drive.
	What is the right level, the right place to draw the line between agent and environment?
	On what basis is one location of the line to be preferred over another? Is there any
	fundamental reason for preferring one location over another, or is it a free choice?
	\subsection*{Solution}
	The line between agent and environment depends on our goal. If we want an agent to decide which path to take to reach our destination faster, we define actions at a higher level (choosing directions). If we want an agent to drive an automobile itself, we define the actions at a lower level (steering wheel, accelerate and brake). The choice depends on problem context, with no fundamental reason to prefer one approach to another.
	
	\subsection{}
	\subsection*{Exercise}
	Give a table analogous to that in Example 3.3, but for $p(s', r\mid s, a)$. It
	should have columns for $s, a, s', r$, and $p(s', r\mid s, a)$, and a row for every 4-tuple for which
	$p(s', r\mid s, a) > 0$.
	\subsection*{Solution}
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		s & a & $s'$  & $r$ & $p(s', r\mid s,a)$ \\
		\hline
		high & search & high & $r_{search}$ & $\alpha$  \\
		high & search & low & $r_{search}$ & $1-\alpha$ \\
		low & search & high  & -3& $1-\varepsilon$ \\
		low & search & low  & $r_{search}$& $\varepsilon$ \\
		high & wait & high & $r_{wait}$& 1  \\
	
	
		low & wait & low & $r_{wait}$ & 1  \\
		low & recharge & high & 0 & 1  \\
	
		\hline
	\end{tabular}
	
	\subsection{}
	\subsection*{Exercise}
	The equations in Section 3.1 are for the continuing case and need to be
	modified (very slightly) to apply to episodic tasks. Show that you know the modifications
	needed by giving the modified version of (3.3).
	\subsection*{Solution}
	$$\sum_{s'\in\mathcal S^+}\sum_{r\in\mathcal R}p(s',r\mid s, a)=1,\quad \text{for all }s\in\mathcal S^+,a\in\mathcal A(s)$$
	
\end{document}